Optimal design for on-farm strip trials --- systematic or randomised?

### 2024-08-23 Revision1/Response.tex

\reviewer{2. My major questions are these (see line 156): For the randomized allocation, was a new randomization generated in each simulation run? Or was the same randomization used in each run. Regarding the systematic design, how was the systematic order determined? Was this the same in each simulation run, and was this equal to that shown in Figure 1? Or was a new systematic order chosen in each run. More importantly, what can be said about the optimal systematic order for the purpose of map estimation? How can this optimum be found? How can optimality be defined? It may well be that the authors do not have an answer to this question. However, the question is relevant, and it is worth at least mentioning in the discussion. At any rate, the choice of systematic order the authors made needs to be explained and justified.}

We appreciate the reviewer for pointing out this crucial confusion in this manuscript. It is not clearly explained in the first draft. We have revised the manuscript by the following amendments:

We added one more subsection \revision{2.3 Performance evaluation} to describe the evaluation of an optimal design:

\revision{To compare the performances of randomised and systematic designs in terms of accurate estimation of the model coefficients using GWR, we use the mean squared errors (MSE) corresponding to all coefficient estimates. The MSE for a coefficient was computed by first taking the differences between the true coefficient, specified in model (3), and the spatially varying estimates of that coefficient produced by GWR, and then averaging these squared differences across all the grid points, shown in equation (12). The lower the MSE, the better the design's performance.}

\revision{The MSE corresponding to the estimation of spatially varying $\beta_{j}$ is given by}
\begin{equation*}\label{eq:mse}
\revision{\text{MSE}_j = \frac{1}{n} \sum_{i=1}^{n} \left( (b_j+u_{ji}) - \hat{\beta}_{ji} \right)^2},
\end{equation*}
\revision{where $j = 0, 1$ for a linear response and $j = 0, 1, 2$ for a quadratic response.}

@@

At the beginning of section 4, we rewrote the paragraph that:

\revision{In this section, we assess the performances of randomised and systematic designs in terms of their utility to accurately estimate the model parameters for both linear and quadratic response models. To this end, we perform 1000 simulations of each of the 24 scenarios, described in the previous section. In each simulation, we first generate the coefficients for all grids and then apply the treatment in each grid to calculate the yield value using the model coefficients. For the treatment order in each iteration, we randomly picked an order of treatments for a single replicate and repeated this sequence across all other replicates to construct a systematic design. For a randomised design, all replicates have random orders of the treatments.}

@@

Thank you for the comment. I have merged the subsections 2.1 and 2.2 to make a clear explanation of the model, and revised the subsection titles to: \revision{2.1 Hierarchical model for generating simulated data} and \revision{2.2 Fitting geographically weighted regression to simulated data}. Additionally, we have added one more subsection that \revision{2.3 Performance evaluation} to explain how to evaluate the performance.

\reviewer{4. At the start of Section 3, the authors state an advantage of data simulated from a parametric model. Are there any disadvantages, and what alternatives could be considered? Perhaps this is also a point for the discussion.}

Thank you for your insightful comment. It is right, while data simulated from a parametric model does have its advantages, it also has certain limitations. One potential disadvantage is that the results are heavily dependent on the assumptions of the parametric model. If these assumptions do not hold, the simulation results may not accurately reflect the real-world scenario.

We have put one paragraph in the discussion section that 
\revision{Our study employs simulation to evaluate the effectiveness of GWR in estimating coefficients for both randomised and systematic designs. However, a potential drawback of using simulation is its high dependency on the assumptions underlying the parametric model. If these assumptions are incorrect or fail to accurately represent real-world conditions, the simulation results may not reliably reflect the actual scenario.}

Additionally, we have revised Section 3, starting with a better description of the data source and why the parameters are chosen at this level. The simulated data aligns with the authentic data from a corn field in Las Rosa. This data has been studied and reported by \textcite{Rakshit2020Novel, Cao2022Bayesian}. The assumption is based on their findings.

@@

\reviewer{5. Also at the start of Section 3, where factors studied in the simulation are listed (from line 156), it is not immediately obvious, if the description of details of the simulations refers to the data simulation or the analysis of simulated data. Clarification would be useful. At this point, it is also still not clear which model was used for simulating the data and which for analysing the data. This only becomes clearer gradually downstream in the paper. I feel it could be made very clear much earlier in the paper.}

We have revised Section 3 for a better and clearer explanation.

\reviewer{6. It may help greatly if the statement of the objectives not made in line 190 comes much earlier.}

We have put a new sentence in the introduction section in line 90: \revision{We subsequently evaluate the efficacy of GWR in accurately estimating the spatially varying treatment effects across these scenarios.}

@@

\reviewer{8. Line 168: Is the 75 for the mid N level a typo? Should this be 70? Why are the levels different from those in Figure 1?}

Thanks for pointing out the discrepancy. We have revised the mistake by updating the labels in the figures and also in the main context:

\revision{Figure 1: The nitrogen treatments with five levels (0, 35, 70, 105 and 140 kg/ha) randomly (left) and systematically (right) allocated into strips in each replicate block.}

In line 72: \revision{We used five evenly spaced nitrogen rates: 0, 35, 70, 105, and 140 kg/ha.}

@@

\reviewer{The general suggestion is to revise the text without so much statistical jargon or add explanations that will make it easier for agronomists to follow/understand.}

We have revised the main text of the manuscript to enhance its readability and comprehension. Additionally, we have streamlined the statistical model sections for simplicity and clarity.

\reviewer{Specific comments: 1) Line 40. Please define OFE here and not in line 46 and 57}

We have now defined OFE when it first appears in the main text in line 45. The revised version is \revision{On-farm experiment (OFE) enables farmers the flexibility ...}.

@@

\reviewer{3) Lines 73-74. I do not see the value of that sentence.}

We have polished this paragraph. The purpose of this sentence is to introduce that a linear model may not be sufficient in capturing the yield curve. That's why we compared linear and quadratic curve in this study.

\reviewer{4) Lines 81-83. These are results and do not fit in the introduction.}

We have rewritten this paragraph to better fit the manuscript by:
\revision{In this study, we generate simulated data for several scenarios, where each scenario is constructed by choosing one component at a time from the following four categories: (i) randomised and systematic designs; (ii) linear and quadratic responses; (iii) model coefficients with low and high correlations; and (iv) spatial variance-covariance matrix
90 among grids given by identity (no spatial trend), AR1 $\bigotimes$ AR1, and Mat\'{e}rn forms. We subsequently evaluate the efficacy of GWR in accurately estimating the spatially varying treatment effects across these scenarios.}

@@

\reviewer{7) 3 Simulation study. More information is needed here. I suggest starting from describing the simulated experiment. For example, I had to read up to line 160 and again after line 166 to understand that the independent variable of interest would be nitrogen fertilizer with 5 levels.}

We have rewritten the simulation section by reordering the paragraphs and making a clearer explanation.

\reviewer{8) Line 172. For someone who is not familiar with systematic design, they would have to read up to line 172 and see figure 1 to understand the difference. I suggest describing what a systematic design is early in the introduction so every reader understands what is being compared.}

We firstly in line 39 inserted the sentence \revision{where treatments are randomly allocated in each replicate} for a randomised design.

In line 41, we rewrote the sentence as follows: \revision{With the primary aim of obtaining unbiased estimates of global treatment effects, randomised designs, which use different
layouts of treatments in each replicate, are routinely used for on-farm strip trials, whereas systematic designs, which use the same layout of treatments in all replicates, are rarely used.}

In line 174, we try to remind the reader by using the following description that \revision{Examples of a randomised design, which uses different orders of treatment in each replicate, and a systematic design, which uses the same order of treatment in all replicates, for this layout are presented in Figure 1.}

@@

\reviewer{10) For more practical purposes, apart from comparing MSE and coefficients, it would be valuable to see two maps with optimal nitrogen rate side-by-side. One map generated by the randomized design and one generated by the systematic design. I suspect that for practical purposes maps will be very similar.}

It's a good point. From the practical point of view, that's the most interests output for growers. So, we added one more sub-section at the end of section 4: 
\revision{4.3 An example of optimal nitrogen map} with the description of the results and two optimal nitrogen maps.

\revision{In practice, growers are more interested in the prescription map that tells them where the appropriate nitrogen should be applied on the paddock. With the application of GWR, we can find the local variations in crop needs, allowing for more precise and efficient nitrogen application. Each grid of the paddock receives the optimal amount of fertiliser. Consequently, this leads to improved crop yields, reduced investment cost and high profit.}

\revision{Figure \ref{fig:yieldmap} is the simulated crop yield map with the assumption of a quadratic response curve and \Matern spatial covariance and low within-grid correlation. These two yield maps have the same coefficients but different yields due to different treatment layouts.}

\begin{figure}[!htp]
\centering
    \begin{subfigure}[t]{0.9\textwidth}
		\centering
		\includegraphics[width=\linewidth]{quad_random_yield_mat.pdf}
		%\caption{}
    \end{subfigure}
    %\hspace{0.05\textwidth}
    \begin{subfigure}[t]{0.9\textwidth}
		\centering
		\includegraphics[width=\linewidth]{quad_syst_yield_mat.pdf}
		%\caption{}
    \end{subfigure}
    \begin{subfigure}[t]{0.9\textwidth}
		\centering
		\includegraphics[width=\linewidth]{quad_diff_yield_mat.pdf}
		%\caption{}
    \end{subfigure}
	\caption{\revision{Simulated yield map of a randomised design (\textit{top}), and a systematic design (\textit{middle}), and the difference of these two designs (\textit{bottom}).}}\label{fig:yieldmap}
\end{figure}

\revision{Figure \ref{fig:optNmap} illustrates an example of the optimal Nitrogen rate (kg/ha) map estimated by GWR with a bandwidth of 9 using the above yield data. The optimal rate at grid $i$ is given by $\hat{N}_i = -\hat{\beta}_{1i}/(2\hat{\beta}_{2i})$ with constraints between 0 and 140, $i=1,\ldots,n$. For the randomised design, GWR underestimated the right part of the paddock. On the contrary, the estimated map from the systematic design is more consistent.}

\begin{figure}[!htp]
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{optN_rand_matB9.pdf}
		%\caption{}
 \end{subfigure}
	\hspace{0.05\textwidth}
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{optN_syst_matB9.pdf}
		%\caption{}
 \end{subfigure}
	\caption{\revision{Optimal Nitrogen rate estimated by GWR from a randomised design (\textit{left}), and a systematic design (\textit{right}).}}\label{fig:optNmap}
\end{figure}

### 2024-08-23 Revision1/main_revision_clear.tex
revision submitted

\newcommand{\revision}[1]{\textcolor{red}{#1}}
\newcommand{\zc}[1]{\textcolor{blue}{#1}}

\usepackage[url=false, isbn=false, eprint=false, backref=true, style= authoryear, backend=biber, maxcitenames=2, giveninits=true, maxbibnames=100, uniquename=init]{biblatex}
%backend=bibtex
\DeclareNameAlias{sortname}{family-given}
\addbibresource{BayesOFE.bib}

@@

\begin{abstract}
CONTEXT OR PROBLEM: Randomised designs are often preferred over systematic designs by agronomists and biometricians. However, for on-farm trials, the choice may depend on the objective of the experiments. If the purpose is to create a prescription map of a continuous input for each plot of a grid covering a large strip trial, a systematic design may be a better choice, but it attracts less discussion and attention.

@@

RESULTS: With the assumption of \revision{a} quadratic response, a systematic design is superior to a randomised design \revision{in terms of achieving lower mean squared errors (MSE) with GWR}. However, with the assumption of \revision{a} linear response, the difference between a systematic design and a randomised design is not significant, regardless of the presence of spatial variation.

CONCLUSIONS: The findings highlight the superiority of systematic designs in producing smooth \revision{spatial} maps of optimal input levels \revision{for quadratic response models in large strip trials, even when impacted by significant spatial variation.}. Additionally, \textcolor{red}{we recommend selecting} fixed bandwidths \revision{in GWR analysis} based on \revision{the plot configurations used in} experimental designs. For a large strip trial, to \revision{produce estimates of spatially-varying treatment effects across strips}, a systemic design should be used as it \revision{allows us to obtain better estimates than those obtained from a randomised design} in post-experiment statistical modelling.

@@

The principle of randomisation was first expounded in 1925 by \textcite{Fisher1934Statistical}, who analysed a few systematically arranged experiments and pointed out that randomisation can provide valid tests of significance subject to appropriate restrictions, such as experimental units arranged in blocks or in rows and columns of a Latin square \parencite{Verdooren2020History}. Traditionally, small-plot trials for agriculture are designed to \revision{obtain unbiased estimates of} treatment effects \revision{using} the completely randomised design (CRD), \zc{where treatments are randomly allocated in each replicate}. More complex designs, such as the randomised complete block design (RCBD), the split-plot design, the strip-plot design and the Latin square design, are also widely used in agricultural experiments \revision{to improve the precision of treatment effect estimates} \parencite{Petersen1994Agricultural}. \revision{With the primary aim of obtaining unbiased estimates of global treatment effects}, randomised designs \zc{, which use different layouts of treatments in each replicate,} are routinely used for on-farm strip trials, \revision{whereas} systematic designs, \zc{which use the same layout of treatments in all replicates,} are rarely used.

@@

%Like conventional agricultural experiments, 
While randomisation is often considered a crucial prerequisite for obtaining valid statistical inferences \parencite{Piepho2013Why}, this is not always the case when the goal of OFE shifts from the conventional analysis. In the application of precision agriculture (PA) \revision{using} variable rate applicators (VRA)\revision{,} a prescription map of the experiment \revision{is required to optimally apply varying treatments across a field} \parencite{Pringle2004FieldScale}. Therefore, in this scenario, the goal of OFE becomes obtaining a smooth \revision{spatial} map showing the optimal level of a controllable input, such as nitrogen rates, across a grid made of rows and columns covering the whole field. \revision{An important point to note here is} that only a single \revision{treatment level} can be directly observed at any one point on the grid, and the response for other levels at the same grid must be interpolated. If a randomised design is conducted, the interpolation distances to locations with treatment levels of interest will vary throughout the field. Such heterogeneous distances increase the uncertainty in the analysis and reduce the efficiency of local prediction. As a result, a systematic design is preferable to a randomised design in this scenario. Unfortunately, this perspective has often been overlooked by researchers, leading to the widespread use of randomised designs.

Analysing a systematic design for the creation of an optimal treatment map is a statistically challenging task. \revision{The true responses} at each point on the grid \revision{corresponding to all the treatment rates are} unknown, and the treatment \revision{producing the optimum response may vary} continuously across the field. \textcite{Cao2022Bayesian} implemented a Bayesian approach with spatially correlated random parameters for \revision{analysing} large systematic strip trials.
\revision{These authors considered} a quadratic response model with both global and local \revision{(}spatially-varying\revision{)} components. However, Bayesian \revision{analysis can be computationally expensive} and \revision{would require at least} preliminary knowledge of Bayesian \revision{inference to interpret the results, which can be extremely demanding} for farmers and agronomists. Alternatively, \textcite{Rakshit2020Novel} adopted a local regression approach, called geographically weighted regression (GWR), to obtain spatially-varying estimates of treatment effects for OFE. Additionally, \textcite{Evans2020Assessment} concluded through simulation studies that GWR is capable of accurately separating variation \revision{in yield response due to treatment from} \revision{the variation that} is not due to the applied treatment. However, their study was limited by the use of a randomised design and the assumption of a linear response \revision{model}. \revision{To compare between the systematic and randomised treatment allocation in the chessboard design,} \textcite{Alesso2021Design} simulated corn yield \revision{response} \revision{for} four nitrogen levels and \revision{estimated the regression} coefficients using GWR. They concluded that systematic designs achieved the best results in most cases. However, the use of chessboard design \revision{often presents several challenges, particularly during harvesting. Harvesters can produce erroneous data due to the abrupt treatment changes between plots} \parencite{Pringle2004FieldScale}. Additionally, the quadratic or plateau feature \revision{in a response model} was not considered in their simulation study.

@@

The underlying template model for the GWR, according to \textcite{Leung2000Statistical}, is given by 
\begin{equation}\label{eq:basicgwr}
	y(s_i) = \beta_0 + \sum_{j=1}^{k} \beta_j \, \revision{x}_j(s_i) + \varepsilon_i, 
\end{equation}
where $\bm{\beta}\revision{ = (\beta_0, \beta_{1}, \ldots, \beta_{k})^{\top}}$ and $\varepsilon_{i} \sim \N(0,\tau^2)$ are the model parameters for the $k$ treatment \revision{levels} and error terms, respectively, at grid $i,\ i=1,\ldots,n$.

\revision{For a query location $s$,} the local log-likelihood \revision{is given by} 
\begin{eqnarray}\label{eq:locallog}
	\log L(s;\beta) = - \frac{1}{2\tau^2}\sum_{i=1}^{n}K(s,s_i)\left( y(s_i) -\beta_0 - \sum_{j=1}^{k}\beta_j \revision{x}_j(s_i) \right)^2 
\end{eqnarray}
with a given kernel function $K(\cdot,\cdot)$, such as Gaussian, exponential, bi-square or tri-cube \parencite{Gollini2015GWmodel}.

@@

In the simulation study, we use a Gaussian kernel. In fact, the kernel \revision{function} is not the crucial factor in the GWR \revision{analysis}. \revision{In} contrast, the bandwidth has a higher influence on estimation.

The optimal bandwidth \revision{for} a GWR model is usually \revision{selected} by the lowest AICc where 
\begin{equation}\label{eq:aicc}
	\mbox{AICc} = 2n\log (\tau^2) + n \log (2\pi) + \frac{n^2+n\tr (S)}{n-2-\tr (S)},
\end{equation}
and $S$ is the matrix with the $i$-th row given by $\revision{X}_i\left( \revision{X}^\top W(s_i) \revision{X} \right)^{-1}\revision{X}^\top W(s_i)$ \parencite{Evans2020Assessment}. Alternatively, as suggested by \textcite{Rakshit2020Novel}, it can be based on the experimental design such that the local regressions capture data covering the full range of treatments.

@@

\zc{To compare the performances of randomised and systematic designs in terms of accurate estimation of the model coefficients using GWR, we use the mean squared errors (MSE) corresponding to all coefficient estimates.} \revision{The MSE for a coefficient was computed by first taking the differences between the true coefficient, specified in model \eqref{eq:underlying}, and the spatially varying estimates of that coefficient produced by GWR \eqref{eq:basicgwr}, and then averaging these squared differences across all the grid points. The lower the MSE, the better the design's performance.} \zc{The advantage of the simulation study is that the actual coefficients of the models are known, so} \revision{possible} \zc{adverse effects of model misspecification can be} \revision{omitted while assessing the performances of different designs on parameter estimation} \parencite{Piepho2013Why}.

@@

\revision{The simulation study is based on the real life data recorded from a corn field in Las Rosas, Argentina. This data set was originally provided by \textcite{Luc2004ASpatial} and can be accessed via the \texttt{R}-package \texttt{agridat} \parencite{White2008Agridat}. In 2001, a systematic design was used, incorporating six rates of nitrogen: 0, 39, 50.6, 75.4, 99.8, and 124.6 kg/ha, in three replicates. Each replicate consists of 93 rows and 6 columns after data preprocessing; see \textcite{Rakshit2020Novel} for further details about the preprocessing steps. The unit of yield is quintals per hectare.}

\revision{Studies by \textcite{Rakshit2020Novel, Cao2022Bayesian} suggest that the yield produced by the maximum nitrogen rate of 124.6 kg/ha may be improved by using a higher rate. Thus, we made some adjustments while selecting the nitrogen rates for our simulation study. We used five evenly spaced nitrogen rates: 0, 35, 70, 105, and 140 kg/ha. Additionally, we increased the number of replicates from three to four. Consequently, the final layout of the trial used in the simulation consisted of 93 rows and 20 columns. Examples of a randomised design, \zc{which uses different orders of treatment in each replicate}, and a systematic design, \zc{which uses the same order of treatment in all replicates}, for this layout are presented in Figure \ref{fig:Nitrogen}.}

\begin{figure}[!htp]
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Expt/Col_RandNitro_V4.pdf}
		%\caption{Treatments are randomly allocated into large strips in each replicate block.}\label{fig:RandNitrogen}
	\end{subfigure}
	\hspace{0.05\textwidth}
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Expt/Col_SystNitro_V4.pdf}
		%\caption{Treatments are systematically allocated into large strips in each replicate block.}\label{fig:SystNitrogen}
	\end{subfigure}
	\caption{\revision{The nitrogen treatments with five levels (0, 35, 70, 105 and 140 kg/ha) randomly (\textit{left}) and systematically (\textit{right}) allocated into strips in each replicate block.}}\label{fig:Nitrogen}
\end{figure}

@@

Figure \ref{fig:Lines} illustrates \revision{the global yield response to Nitrogen} for the linear and quadratic relationships.
\begin{figure}[H]
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Expt/LinlinesV2.pdf}
		%\caption{}
        \end{subfigure}
	\hspace{0.05\textwidth}
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Expt/QualinesV2.pdf}
		%\caption{}
        \end{subfigure}
	\caption{\revision{The global linear relationship of yield and nitrogen is $y=65+0.05N$ (\textit{left}), and the global quadratic relationship between yield and nitrogen is $y=65+0.05N-0.003N^2$ (\textit{right}).}}\label{fig:Lines}
\end{figure}

@@

\revision{In this section, we assess the performances of randomised and systematic designs in terms of their utility to accurately estimate the model parameters for both linear and quadratic response models. To this end, we perform 1\,000 simulations of each \revision{of the 24} scenarios\zc{, described} in the previous section.} \zc{In each simulation, we first generated the coefficients for all grids and then applied the treatment in each grid to calculate the yield value using the model coefficients. For the treatments in all grids, we randomly picked an order of treatments for a single replicate and repeated this sequence across all other replicates to construct a systematic design. For a randomised design, all replicates have different orders of the treatments.} In Section~\ref{Sec:MSE}, the mean squared errors are compared between the two designs for different \revision{factors, including the choice of} bandwidth, parameter correlation, and spatial covariance matrix. Section~\ref{Sec:anova} uses \revision{the} analysis of variance (ANOVA) to  \revision{assess} the significance of the factors \revision{considered} in the simulation \revision{study}. %\st{subsection} Section~\ref{Sec:bandselect} \st{states} \revision{presents} the \st{performance of} \revision{results of} bandwidth selection using AICc.

@@

Curtin Biometry and Data Analytics (CBADA) gratefully acknowledges the support from the Grains Research and Development Corporation of Australia (GRDC).

>>>>

\newcommand{\revision}[1]{\textcolor{black}{#1}}
\newcommand{\zc}[1]{\textcolor{black}{#1}}

\usepackage[url=false, isbn=false, eprint=false, backref=true, style= authoryear, backend=bibtex, maxcitenames=2, giveninits=true, maxbibnames=100, uniquename=init]{biblatex}
%backend=bibtex
\DeclareNameAlias{sortname}{family-given}
\addbibresource{BayesOFE.bib}

@@

\begin{abstract}
CONTEXT OR PROBLEM: Randomised designs are often preferred over systematic designs by agronomists and biometricians. For on-farm trials, \zc{however}, the choice may depend on the objective of the experiments. If the purpose is to create a prescription map of a continuous input for each plot of a grid covering a large strip trial, a systematic design may be a better choice, but it attracts less discussion and attention.

@@

RESULTS: With the assumption of \revision{a} quadratic response, a systematic design is superior to a randomised design \revision{in terms of achieving lower mean squared errors (MSE) with GWR}. \zc{With} the assumption of \revision{a} linear response, the difference \zc{of MSE} between a systematic design and a randomised design is not significant, regardless of the presence of spatial variation.

CONCLUSIONS: The findings highlight the superiority of systematic designs in producing smooth \revision{spatial} maps of optimal input levels \revision{for quadratic response models in large strip trials, even when impacted by significant spatial variation.} Additionally, \revision{we recommend selecting} fixed bandwidths \revision{in GWR analysis} based on \revision{the plot configurations used in} experimental designs. For a large strip trial, to \revision{produce estimates of spatially-varying treatment effects across strips}, a systemic design should be used as it \revision{allows us to obtain better estimates than those obtained from a randomised design} in post-experiment statistical modelling.

@@

The principle of randomisation was first expounded in 1925 by \textcite{Fisher1934Statistical}, who analysed a few systematically arranged experiments and pointed out that randomisation can provide valid tests of significance subject to appropriate restrictions, such as experimental units arranged in blocks or in rows and columns of a Latin square \parencite{Verdooren2020History}. Traditionally, small-plot trials for agriculture are designed to \revision{obtain unbiased estimates of} treatment effects \revision{using} the completely randomised design, \zc{where treatments are randomly allocated into plots}. More complex designs, such as the randomised complete block design, the split-plot design, the strip-plot design and the Latin square design, are also widely used in agricultural experiments \revision{to improve the precision of treatment effect estimates} \parencite{Petersen1994Agricultural}. \revision{With the primary aim of obtaining unbiased estimates of global treatment effects}, randomised designs \zc{, which use different layouts of treatments in each replicate,} are routinely used for on-farm strip trials, \revision{whereas} systematic designs, \zc{which use the same layout of treatments in all replicates,} are rarely used.

@@

%Like conventional agricultural experiments, 
While randomisation is often considered a crucial prerequisite for obtaining valid statistical inferences \parencite{Piepho2013Why}, this is not always the case when the goal of OFE shifts from the conventional analysis. In the application of precision agriculture \revision{using} variable rate applicators\revision{,} a prescription map of the experiment \revision{is required to optimally apply varying treatments across a field} \parencite{Pringle2004FieldScale}. Therefore, in this scenario, the goal of OFE becomes obtaining a smooth \revision{spatial} map showing the optimal level of a controllable input, such as nitrogen rates, across a grid made of rows and columns covering the whole field. \revision{An important point to note here is} that only a single \revision{treatment level} can be directly observed at any one point on the grid, and the response for other levels \zc{in} the same grid must be interpolated. If a randomised design is conducted, the interpolation distances to locations with treatment levels of interest will vary throughout the field. Such heterogeneous distances increase the uncertainty in the analysis and reduce the efficiency of local prediction. As a result, a systematic design is preferable to a randomised design in this scenario. Unfortunately, this perspective has often been overlooked by researchers, leading to the widespread use of randomised designs.

Analysing a systematic design for the creation of an optimal treatment map is a statistically challenging task. \revision{The true responses} at each point on the grid \revision{corresponding to all the treatment rates are} unknown, and the treatment \revision{producing the optimum response may vary} continuously across the field. \textcite{Cao2022Bayesian} implemented a Bayesian approach with spatially correlated random parameters for \revision{analysing} large systematic strip trials.
\revision{These authors considered} a quadratic response model with both global and local \revision{(}spatially-varying\revision{)} components. However, Bayesian \revision{analysis can be computationally expensive} and \revision{would require at least} preliminary knowledge of Bayesian \revision{inference to interpret the results, which can be extremely demanding} for farmers and agronomists. Alternatively, \textcite{Rakshit2020Novel} adopted a local regression approach, called geographically weighted regression (GWR), to obtain spatially-varying estimates of treatment effects for OFE. Additionally, \textcite{Evans2020Assessment} concluded through simulation studies that GWR is capable of accurately separating variation \revision{in yield response due to treatment from} \revision{the variation that} is not due to the applied treatment. \zc{The limitations in} their study \zc{are} the use of a randomised design and the assumption of a linear response \revision{model}. \revision{To compare between the systematic and randomised treatment allocation in the chessboard design,} \textcite{Alesso2021Design} simulated corn yield \revision{response} \revision{for} four nitrogen levels and \revision{estimated the regression} coefficients using GWR. They concluded that systematic designs achieved the best results in most cases. However, the use of chessboard design \revision{often presents several challenges, particularly during harvesting. Harvesters can produce erroneous data due to the abrupt treatment changes between plots} \parencite{Pringle2004FieldScale}. Additionally, the quadratic or plateau feature \revision{in a response model} was not considered in their simulation study.

@@

The underlying template model for GWR is given by 
\begin{equation}\label{eq:basicgwr}
	y(s_i) =  \beta_0 + \sum_{j=1}^{k} \beta_j \, \revision{x}_j(s_i) + \varepsilon_i, 
\end{equation}
where $\bm{\beta}\revision{ = (\beta_0, \beta_{1}, \ldots, \beta_{k})^{\top}}$ are model parameters corresponding to the $k$ treatment \revision{levels} and $\varepsilon_{i} \sim \N(0,\tau^2)$,  $i=1,\ldots,n$,  are independent and identically distributed error terms at $n$ grid points.

\revision{For a query location $s$,} the local log-likelihood \revision{is given by} 
\begin{eqnarray}\label{eq:locallog}
	\log L(s; \bm{\beta}) = - \frac{1}{2\tau^2}\sum_{i=1}^{n}K(s,s_i)\left( y(s_i) -\beta_0 - \sum_{j=1}^{k}\beta_j \revision{x}_j(s_i) \right)^2 
\end{eqnarray}
where $K(\cdot,\cdot)$ is a given kernel function, such as Gaussian, exponential, bi-square or tri-cube \parencite{Gollini2015GWmodel}.

@@

\revision{To obtain GWR estimates of model parameters} in the simulation study, we have used a Gaussian kernel. In fact, the kernel \revision{function} is not the crucial factor in the GWR \revision{analysis}. \revision{In} contrast, the bandwidth has a higher influence on the estimates.

The optimal bandwidth \revision{for} a GWR model is usually \revision{selected} by the lowest AICc, which is given by 
\begin{equation}\label{eq:aicc}
	\mbox{AICc} = 2n\log (\tau^2) + n \log (2\pi) + \frac{n^2+n\tr (S)}{n-2-\tr (S)},
\end{equation}
where $S$ is the matrix with the $i$-th row given by $\revision{X}_i\left( \revision{X}^\top W(s_i) \revision{X} \right)^{-1}\revision{X}^\top W(s_i)$ \parencite{Evans2020Assessment}, \zc{and $\tr(\cdot)$ is the trace of a square matrix returning the sum of the elements on the main diagonal.} Alternatively, as suggested by \textcite{Rakshit2020Novel}, it can \zc{be chosen according to} the experimental design such that the local regressions capture data covering the full range of treatments.

@@

\zc{To compare the performances of randomised and systematic designs in terms of accurate estimation of the model coefficients using GWR, we use the mean squared errors (MSE) corresponding to all coefficient estimates.} \revision{The MSE for a coefficient was computed by first taking the differences between the true coefficient, specified in model \eqref{eq:underlying}, and the spatially varying estimates of that coefficient produced by GWR, and then averaging these squared differences across all the grid points, shown in equation \eqref{eq:mse}. The lower the MSE, the better the design's performance.}

\revision{The MSE corresponding to the estimation of spatially varying $\beta_{j}$ is given by}
\begin{equation}\label{eq:mse}
\zc{\text{MSE}_j = \frac{1}{n} \sum_{i=1}^{n} \left( (b_j+u_{ji}) - \hat{\beta}_{ji} \right)^2},
\end{equation}
\zc{where $j = 0, 1$ for a linear response and $j = 0, 1, 2$ for a quadratic response.}

%This part is not needed and wrong also in our context and confusing....\zc{The advantage of the simulation study is that the actual coefficients of the models are known, so} \revision{possible} \zc{adverse effects of model misspecification can be} \revision{omitted while assessing the performances of different designs on parameter estimation} \parencite{Piepho2013Why}.

@@

\revision{The simulation study is performed using realistic values for the model parameters, which are selected based on the analysis results of a real-life data recorded from a corn field in Las Rosas, Argentina. This data set was originally provided by \textcite{Luc2004ASpatial} and can be accessed via the \texttt{R}-package \texttt{agridat} \parencite{White2008Agridat}. In 2001, a systematic design was used, incorporating six rates of nitrogen: 0, 39, 50.6, 75.4, 99.8, and 124.6 kg/ha, in three replicates. Each replicate consists of 93 rows and 6 columns after data preprocessing; see \textcite{Rakshit2020Novel} for further details about the preprocessing steps. The unit of yield is quintals per hectare.}

\revision{Studies by \textcite{Rakshit2020Novel, Cao2022Bayesian} suggest that the yield produced by the maximum nitrogen rate of 124.6 kg/ha may be improved by using a higher rate. Thus, we have made some adjustments while selecting the nitrogen rates for our simulation study. We use five evenly-spaced nitrogen rates: 0, 35, 70, 105, and 140 kg/ha. Additionally, we increase the number of replicates from three to four. Consequently, the final layout of the trial used in the simulation consists of 93 rows and 20 columns. Examples of a randomised design, \zc{which uses different orders of treatment in each replicate}, and a systematic design, \zc{which uses the same order of treatment in all replicates}, for this layout are presented in Figure \ref{fig:Nitrogen}.}

\begin{figure}[!htp]
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Col_RandNitro_V4.pdf}
		%\caption{Treatments are randomly allocated into large strips in each replicate block.}\label{fig:RandNitrogen}
	\end{subfigure}
	\hspace{0.05\textwidth}
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Col_SystNitro_V4.pdf}
		%\caption{Treatments are systematically allocated into large strips in each replicate block.}\label{fig:SystNitrogen}
	\end{subfigure}
	\caption{\revision{The nitrogen treatments with five levels (0, 35, 70, 105 and 140 kg/ha) randomly (\textit{left}) and systematically (\textit{right}) allocated into strips in each replicate block.}}\label{fig:Nitrogen}
\end{figure}

@@

Figure \ref{fig:Lines} illustrates \revision{the global yield response to Nitrogen} for the linear and quadratic relationships.
\begin{figure}[H]
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{LinlinesV2.pdf}
		%\caption{}
 \end{subfigure}
	\hspace{0.05\textwidth}
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{QualinesV2.pdf}
		%\caption{}
 \end{subfigure}
	\caption{\revision{The global linear relationship of yield and nitrogen is $y=65+0.05N$ (\textit{left}), and the global quadratic relationship between yield and nitrogen is $y=65+0.05N-0.003N^2$ (\textit{right}).}}\label{fig:Lines}
\end{figure}

@@

\revision{In this section, we assess the performances of randomised and systematic designs in terms of their utility to accurately estimate the model parameters for both linear and quadratic response models. To this end, we perform 1000 simulations of each \revision{of the 24} scenarios\zc{, described} in the previous section.} \zc{In each simulation, we first generate the coefficients for all grids and then apply the treatment in each grid to calculate the yield value using the model coefficients. For the treatment order in each iteration, we randomly picked an order of treatments for a single replicate and repeated this sequence across all other replicates to construct a systematic design. For a randomised design, all replicates have random orders of the treatments.}

% In Section~\ref{Sec:MSE}, the MSEs are compared between the two designs for different \revision{factors, including the choice of} bandwidth, parameter correlation, and spatial covariance matrix. % Section~\ref{Sec:anova} uses \revision{the} analysis of variance (ANOVA) to  \revision{assess} the significance of the factors \revision{considered} in the simulation \revision{study}. %\st{subsection} Section~\ref{Sec:bandselect} \st{states} \revision{presents} the \st{performance of} \revision{results of} bandwidth selection using AICc.

@@

Curtin Biometry and \zc{Agricultural} Data Analytics (CBADA) gratefully acknowledges the support from the Grains Research and Development Corporation of Australia (GRDC).
